A Partitioning Algorithm for Maximum Common Subgraph Problems\thanks{This work was supported by a pile of money from a funding agency.}

### 2017-02-16 paper/paper.tex
Move move move
Clean up experiments some more

\begin{figure}[h]
    \centering
    \subfigure[][Unlabelled, undirected instances] {
        \centering
        \includegraphics*{gen-graph-plain-cumulative.pdf}
        \label{figure:plain-cumulative}
    }

    \subfigure[][Vertex and edge labelled directed instances] {
        \centering
        \includegraphics*{gen-graph-33ved-cumulative.pdf}
        \label{figure:33ved-cumulative}
    }
    \caption{Cumulative numbers of instances solved over time for the maximum
    common subgraph problem.}\label{figure:mcs-cumulative}
\end{figure}

\paragraph{Unlabelled, undirected}
\cref{figure:plain-cumulative} shows a plot of cumulative run times (x-axis)
against number of problem instances solved (y-axis).  There are five contours:
the clique encoding \citep{DBLP:conf/cp/McCreeshNPS16}, CP-FC
\citep{DBLP:conf/cp/NdiayeS11}, \McSplit\, AND TWO OTHERS.  WE NEED CITATIONS
FOR THESE AND ALSO NEED TO CLEAN UP THE LABELS ON THE GRAPHS.  We may compare
the speed of two algorithms using the horizontal distance between their curves.
For example, we could solve 2000 of the 4110 unlabelled undirected instances
using the \McSplit\ algorithm if a time limit of 0.5 seconds per instance were
imposed.  Its nearest competitor, CP-FC, would require a time limit of over 24
seconds per instance to solve the same number of instances.  For any given
number of instances, \McSplit\ is comfortably more than an order of magnitude
faster than its nearer competitor.  Moreover, there are few instances in this
set for which \McSplit\ is not the fastest solver; of the 3506 instances that
could be solved by at least one of \McSplit, CP-FC and clique in less than than
1000 seconds, there were only 126 instances on which \McSplit\ was not strictly
faster than the other two solvers.

@@

\paragraph{Unlabelled, undirected, connected} This class of instances are shown
in \cref{figure:plain-connected-cumulative}.  These results are very similar to
the corresponding experiment in \cref{figure:plain-cumulative} in which the
subgraph is not required to be connected.

@@

\begin{figure}[t]
    \centering
    \subfigure[][MCS unlabelled undirected instances] {
        \centering
        \includegraphics*{gen-graph-plain-connected-cumulative.pdf}
        \label{figure:plain-connected-cumulative}
    }

    \subfigure[][MCS 33\% vertex and edge labelled undirected instances] {
        \centering
        \includegraphics*{gen-graph-33ve-connected-cumulative.pdf}
        \label{figure:33ve-connected-cumulative}
    }
    \caption{Cumulative run times, connected variant}
    \label{figure:mcs-connected-cumulative}
\end{figure}

@@

@@

\begin{figure}[h]
    \centering
    \includegraphics*{gen-graph-sip-cumulative.pdf}
    \caption{Cumulative run times, SIP instances}\label{figure:sip-cumulative}
\end{figure}

>>>>

\begin{figure}[t]
    \centering
    \subfigure[][Unlabelled, undirected instances] {
        \centering
        \includegraphics*{gen-graph-plain-cumulative.pdf}
        \label{figure:plain-cumulative}
    }

    \subfigure[][Vertex and edge labelled, directed instances] {
        \centering
        \includegraphics*{gen-graph-33ved-cumulative.pdf}
        \label{figure:33ved-cumulative}
    }
    \caption{Cumulative numbers of instances solved over time for the maximum
    common subgraph problem.}\label{figure:mcs-cumulative}
\end{figure}

?? kdown only does undirected unlabelled unconnected

?? There are five contours:
the clique encoding \citep{DBLP:conf/cp/McCreeshNPS16}, CP-FC
\citep{DBLP:conf/cp/NdiayeS11}, \McSplit\, AND TWO OTHERS.  WE NEED CITATIONS
FOR THESE AND ALSO NEED TO CLEAN UP THE LABELS ON THE GRAPHS.

\paragraph{Unlabelled, undirected}
\cref{figure:plain-cumulative} shows a plot of cumulative run times (x-axis)
against number of problem instances solved (y-axis).  We may compare
the speed of two algorithms using the horizontal distance between their curves.
For example, we could solve 2000 of the 4110 unlabelled undirected instances
using the \McSplit\ algorithm if a time limit of 0.5 seconds per instance were
imposed.  Its nearest competitor, CP-FC, would require a time limit of over 24
seconds per instance to solve the same number of instances.  For any given
number of instances, \McSplit\ is comfortably more than an order of magnitude
faster than its nearer competitor.  Moreover, there are few instances in this
set for which \McSplit\ is not the fastest solver; of the 3506 instances that
could be solved by at least one of \McSplit, CP-FC and clique in less than than
1000 seconds, there were only 126 instances on which \McSplit\ was not strictly
faster than the other two solvers.

@@

\paragraph{Unlabelled, undirected, connected} This class of instances are shown
in \cref{figure:plain-connected-cumulative} (again, ??kdown does not support the connected problem).  These results are very similar to
the corresponding experiment in \cref{figure:plain-cumulative} in which the
subgraph is not required to be connected.

@@

\begin{figure}[t]
    \centering
    \subfigure[][Unlabelled, undirected, connected instances] {
        \centering
        \includegraphics*{gen-graph-plain-connected-cumulative.pdf}
        \label{figure:plain-connected-cumulative}
    }

    \subfigure[][Vertex and edge labelled, undirected, connected instances] {
        \centering
        \includegraphics*{gen-graph-33ve-connected-cumulative.pdf}
        \label{figure:33ve-connected-cumulative}
    }
    \caption{Cumulative numbers of instances solved over time for the maximum
    common connected subgraph problem.} \label{figure:mcs-connected-cumulative}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics*{gen-graph-sip-cumulative.pdf}
    \caption{Cumulative run times, SIP instances}\label{figure:sip-cumulative}
\end{figure}

@@
